A lottery model of density-dependent selection

### 2017-10-13 manuscript.tex
latest

Some of the earliest explicit discussions of the interplay between ecology and evolution appear in the density-dependent selection literature \citep{travis_2013}.

Much of this work grew out of MacArthur's $r$/$K$-selection scheme \citep{macarthur_1962,macarthur_1967} in which $r$-selection favors faster growth at low density, whereas $K$-selection favors the ability to keep growing at high density.

>>>>

The density-dependent selection literature contains some of the earliest explicit analyses of the interplay between ecology and evolution \citep{travis_2013}. This work is most famously associated with MacArthur's $r$/$K$ scheme \citep{macarthur_1962,macarthur_1967} in which $r$-selection favors faster growth at low density, whereas $K$-selection favors the ability to keep growing at high density.

Starting with Kostitzin's
